Converting LaTeX R Journal Articles into Rmarkdown using texor and rebib

### 2023-07-02 texor.Rmd
Updated title and `\CRANpkg{}` usage

---
title: "Converting LaTeX R Journal Articles into RJ-web-articles"
date: "2022-11-09"
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  # see ?rjournal_article for more information
  - name: Abhishek Ulayil
    affiliation: Student, Institute of Actuaries of India
    address:
    - Mumbai, India
    orcid: 0009-0000-6935-8690
    email: perricoq@outlook.com
  - name: Mitch O'Hara-Wild
    affiliation: Monash University
    address:
    - Melbourne, Australia
    orcid: 0000-0001-6729-7695
    email: mail@mitchelloharawild.com
  - name: Christophe Dervieux
    affiliation: Posit PBC
    address:
    - Paris, France
    orcid: 0000-0003-4474-2498
    email: christophe.dervieux@gmail.com
  - name: Heather Turner
    affiliation: University of Warwick
    address:
    - Newport, United Kingdom
    orcid: 0000-0002-1256-3375
    email: ht@heatherturner.net
  - name: Dianne Cook
    affiliation: Monash University
    address:
    - Melbourne, Australia
    orcid: 0000-0002-3813-7155
    email: dicook@monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    web_only: yes
    self_contained: yes
    toc: no
bibliography: RJreferences.bib

@@

Pandoc is a versatile document conversion program written in Haskell that is core
to numerous documentation systems, including Rmarkdown and Quarto. Pandoc first 
converts a document into an abstract syntax tree. From this, it can convert to a
different format, including custom ones. Although creating bespoke writers/readers
in Lua can be challenging, pandoc includes filters that allow users to customise 
the output generated based on matching patterns plus some logic to modify them.

The Texor package uses these filters heavily, even for simple tasks like choosing
which supporting figures to copy. A Lua filter constructs a list of image paths, 
stores them momentarily and the package uses this data to copy images.

@@

# Texor package converting LaTeX to Rmarkdown

@@

# Rebib is in charge of the bibliography

@@

It was initially a part of the \CRANpkg{texor} package, as those functions grew 
in features and became more involved; at that point, it made sense to move those
functions as a separate package. Initially, there were some reservations about 
the usage of rebib and its stability with various formats. However,
the package has improved over time and proven to be a good performer.

Rebib's best feature is its ability to merge bibliographies from both the 
LaTeX and BibTeX files. \CRANpkg{rebib} saves authors from manually 
converting to BibTeX format.

# getting started

@@

# supplementary Materials
 github repos for the packages, rjtools

>>>>

---
title: "Converting LaTeX R Journal Articles into Rmarkdown using texor and rebib"
date: "2022-11-09"
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  # see ?rjournal_article for more information
  - name: Abhishek Ulayil
    affiliation: Student, Institute of Actuaries of India
    address:
    - Mumbai, India
    orcid: 0009-0000-6935-8690
    email: perricoq@outlook.com
  - name: Mitch O'Hara-Wild
    affiliation: Monash University
    address:
    - Melbourne, Australia
    orcid: 0000-0001-6729-7695
    email: mail@mitchelloharawild.com
  - name: Christophe Dervieux
    affiliation: Posit PBC
    address:
    - Paris, France
    orcid: 0000-0003-4474-2498
    email: christophe.dervieux@gmail.com
  - name: Heather Turner
    affiliation: University of Warwick
    address:
    - Newport, United Kingdom
    orcid: 0000-0002-1256-3375
    email: ht@heatherturner.net
  - name: Dianne Cook
    affiliation: Monash University
    address:
    - Melbourne, Australia
    orcid: 0000-0002-3813-7155
    email: dicook@monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    web_only: yes
    self_contained: yes
    toc: no
bibliography: RJreferences.bib

@@

Pandoc is a versatile document conversion program written in Haskell that is core
to numerous documentation systems, including Rmarkdown and Quarto. Pandoc first 
converts a document into an abstract syntax tree. From this, it can convert to a
different format, including custom ones. Although creating bespoke writers/readers
in Lua can be challenging, pandoc includes filters that allow users to customize 
the output generated based on matching patterns plus some logic to modify them.

The \CRANpkg{texor} package uses these filters heavily, even for simple tasks like choosing
which supporting figures to copy. A Lua filter constructs a list of image paths, 
stores them momentarily and the package uses this data to copy images.

@@

# Converting LaTeX to Markdown

@@

# Managing bibliography using \CRANpkg{rebib}

@@

It was initially a part of the \CRANpkg{texor} package, as those functions grew 
in features and became more involved; at that point, it made sense to move those
functions as a separate package. Initially, there were some reservations about 
the usage of \CRANpkg{rebib} and its stability with various formats. However,
the package has improved over time and proven to be a good performer.

# Getting started

@@

# Supplementary materials
 github repos for the packages, rjtools
